Gut-resident microorganisms and their genes are associated with cognition and neuroanatomy in children

### 2023-10-04 manuscript/main.tex
updated table 5

\begin{table}[!h]
    \begin{center}
    \begin{tabular}{|r|r|r|}
      \hline\hline
      \textbf{Statistic} & \textbf{MAPE} & \textbf{R} \\\hline
      Mean & 0.073 & 0.137 \\
      Standard deviation & 0.028 & 0.137 \\
      Maximum & 0.206 & 0.605 \\
      75th percentile & 0.082 & 0.195 \\
      50th percentile & 0.067 & 0.134 \\
      25th percentile & 0.057 & 0.062 \\
      Minimum & 0.035 & -0.147 \\\hline\hline
    \end{tabular}
    \caption{\label{tab:neuro}Summary statistics for the neuroanatomy prediction benchmarks.
    Mean absolute proportional error (MAPE) and correlation coeficient (R)
    of test-set preditions are reported accross models for all brain regions.
    Complete list of values can be found on Table S2.}
    \end{center}
\end{table}

>>>>

\begin{table}[!h]
    \begin{center}
    \begin{tabular}{|r|r|r|}
      \hline\hline
      \textbf{Statistic} & \textbf{MAPE} & \textbf{R} \\\hline
      Mean & 0.069 & 0.206 \\
      Standard deviation & 0.015 & 0.099 \\
      Maximum & 0.11 & 0.444 \\
      75th percentile & 0.076 & 0.262 \\
      50th percentile & 0.066 & 0.206 \\
      25th percentile & 0.057 & 0.16 \\
      Minimum & 0.046 & 0.005 \\\hline
    \end{tabular}
    \caption{\label{tab:neuro}Summary statistics for the neuroanatomy prediction benchmarks.
    Mean absolute proportional error (MAPE) and correlation coeficient (R)
    of test-set preditions are reported accross models for all brain regions.
    Complete list of values can be found on Table S2.}
    \end{center}
\end{table}
